---
title: "Predict if a car purchased at auction is a lemon"
output:
  html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(plotly)
library(ggpubr)
library(reshape2)
library(knitr)
library(dplyr)
library(kableExtra)
library(descr)
library(table1)
library(RColorBrewer)
my.col <- brewer.pal(n = 8, name = 'RdBu')
setwd("D:/大三/下/巨量")
cars <- read.table("training.csv", sep=',', header=T)
vars <- read.csv("dictionary.csv", sep=',', header=T)
attach(cars)
```

## Data Source and Introduction
<font size="3">**Name:**</font>
  
Don't Get Kicked!!

<font size="3">**From:**</font>

Kaggle Competition

<font size="3">**Introduction:**</font>

This data set was published by Carvana at www.kaggle.com, which refers to the considerations a buyer has to make in order to buy a used car that's in the best possible conditions.

<font size="3">**Source:**</font>
  
Carvana

<font size="3">**URL:**</font>
  
<https://www.kaggle.com/c/DontGetKicked/data>.

##Variable Description

<font size="3">**Independent Variables**</font>
```{r indep}
kable(vars[-4, ], table.attr='class="table-fixed-header"', row.names = F) %>%
  kable_styling(full_width=F)
```

<font size="3">**Dependent Variables**</font>
```{r dep}
kable(vars[4, ], table.attr='class="table-fixed-header"', row.names=F) %>%
  kable_styling(position="left", full_width=T)
```

## Data Appearance

```{r data}
kable(head(cars), table.attr='class="table-fixed-header"') %>%
  kable_styling() %>%
  scroll_box(height=F)
```

## Summary of Variable
<font size="3">**Dependent Variable**</font>
```{r response}

dep <- as.data.frame(table(IsBadBuy))
kable(dep, table.attr='class="table-fixed-header"', align="l") %>%
  kable_styling(full_width=F, position="float_left")

```

```{r response plot, echo=FALSE}

barplot(table(IsBadBuy), col=brewer.pal(n = 8, name = "RdBu"))

```

```{r trans, include=FALSE}

cars$MMRAcquisitionAuctionAveragePrice <- as.numeric(as.character(MMRAcquisitionAuctionAveragePrice))
cars$MMRAcquisitionAuctionCleanPrice <- as.numeric(as.character(MMRAcquisitionAuctionCleanPrice))
cars$MMRAcquisitionRetailAveragePrice <- as.numeric(as.character(MMRAcquisitionRetailAveragePrice))
cars$MMRAcquisitionRetailCleanPrice <- as.numeric(as.character(MMRAcquisitionRetailCleanPrice))
cars$MMRCurrentAuctionAveragePrice <- as.numeric(as.character(MMRCurrentAuctionAveragePrice))
cars$MMRCurrentAuctionCleanPrice <- as.numeric(as.character(MMRCurrentAuctionCleanPrice))
cars$MMRCurrentRetailAveragePrice <- as.numeric(as.character(MMRCurrentRetailAveragePrice))
cars$MMRCurrentRetailCleanPrice <- as.numeric(as.character(MMRCurrentRetailCleanPrice))
cars$VehicleAge<-as.numeric(as.character((cars$VehicleAge)))
cars$VehOdo<-as.numeric(as.character((cars$VehOdo)))
cars$VNZIP<-as.numeric(as.character((cars$VNZIP)))
cars$VehBCost<-as.numeric(as.character((cars$VehBCost)))
cars$WarrantyCost<-as.numeric(as.character((cars$WarrantyCost)))

cars$VNZIP <- as.factor(cars$VNZIP)
cars$VehYear <- as.factor(cars$VehYear)
cars$VehicleAge <- as.factor(cars$VehicleAge)
cars$IsOnlineSale <- as.factor(cars$IsOnlineSale)

levels(cars$Transmission)[1] <- "NULL"
levels(cars$Transmission)[3] <- "MANUAL"

label(cars$Auction) <- "Auction"
label(cars$VehYear) <- "VehYear"
label(cars$Make) <- "Make"
label(cars$Color) <- "Color"
label(cars$Transmission) <- "Transmission"
label(cars$WheelType) <- "WheelType"
label(cars$Nationality) <- "Nationality"
label(cars$Size) <- "Size"
label(cars$TopThreeAmericanName) <- "TopThreeAmericanName"
label(cars$PRIMEUNIT) <- "PRIMEUNIT"
label(cars$AUCGUART) <- "AUCGUART"
label(cars$VNST) <- "VNST"
label(cars$IsOnlineSale) <- "IsOnlineSale"

attach(cars)
```

```{r table1, include=F}
cate.table <- table1(
  ~ Auction
  + VehYear
  + VehicleAge
  + Make
  + Color
  + Transmission
  + WheelType
  + Nationality
  + Size
  + TopThreeAmericanName
  + PRIMEUNIT
  + AUCGUART
  + VNST
  + IsOnlineSale 
  + VNZIP|
    IsBadBuy,
  data = cars,
  overall="Total" 
)
cont.table <- table1(
  ~ VehOdo
  + MMRAcquisitionAuctionAveragePrice
  + MMRAcquisitionAuctionCleanPrice
  + MMRAcquisitionRetailAveragePrice
  + MMRAcquisitionRetailCleanPrice
  + MMRCurrentAuctionAveragePrice
  + MMRCurrentAuctionCleanPrice
  + MMRCurrentRetailAveragePrice
  + MMRCurrentRetailCleanPrice
  + VehBCost
  + WarrantyCost |
    IsBadBuy,
  data = cars
)
```

# Tables of Categorical Variables{.tabset}

## Categorical
```{r cate, echo=FALSE}
cate.table
```

## Continous
```{r cont, echo=FALSE}
cont.table
```

```{r balloonplot, include=F}

balloon <- function(x){
  df <- table(x, IsBadBuy)
  df <- as.matrix.data.frame(df)
  row.names(df) <- as.factor(levels(x))
  colnames(df) <- c("Good", "Bad")
  ggballoonplot(df, fill = "value")+
    scale_fill_viridis_c(option = "C")+
    scale_fill_gradientn(colors = my.col)
}

many.cate <- cbind.data.frame(Make, Color, Size, VNST, VNZIP)

```

```{r barplots, include=F}
bar <- function(data){
  df <- table(data, IsBadBuy)
  df <- as.data.frame(df)
  levels(df$IsBadBuy) <- c("Good", "Bad")
  ggplot(df, aes(x=data, y=Freq, fill=IsBadBuy)) +
    geom_bar(stat="identity", position=position_dodge())
}
less.cate <- cbind.data.frame(Auction, VehYear, VehicleAge, Transmission, WheelType, Nationality, TopThreeAmericanName, PRIMEUNIT, AUCGUART, IsOnlineSale)

```


# Plots of Categorical Variables{.tabset}

## Make
```{r ball1, echo=FALSE}
ggplotly(balloon(many.cate[, 1]))
```

## Color
```{r ball2, echo=FALSE}
ggplotly(balloon(many.cate[, 2]))
```

## Size
```{r ball3, echo=FALSE}
ggplotly(balloon(many.cate[, 3]))
```

## VNST
```{r ball4, echo=FALSE}
ggplotly(balloon(many.cate[, 4]))
```

## VNZIP
```{r ball5, echo=FALSE}
ggplotly(balloon(many.cate[, 5]))
```

## Auction
```{r bar1, echo=FALSE}
ggplotly(bar(less.cate[, 1]))
```

## VehYear
```{r bar2, echo=FALSE}
ggplotly(bar(less.cate[, 2]))
```

## VehicleAge
```{r bar3, echo=FALSE}
ggplotly(bar(less.cate[, 3]))
```

## Transmission
```{r bar4, echo=FALSE}
ggplotly(bar(less.cate[, 4]))
```

## WheelType
```{r bar5, echo=FALSE}
ggplotly(bar(less.cate[, 5]))
```

## Nationality
```{r bar6, echo=FALSE}
ggplotly(bar(less.cate[, 6]))
```

## TopThreeAmericanName
```{r bar7, echo=FALSE}
ggplotly(bar(less.cate[, 7]))
```

## PRIMEUNIT
```{r bar8, echo=FALSE}
ggplotly(bar(less.cate[, 8]))
```

## AUCGUART
```{r bar9, echo=FALSE}
ggplotly(bar(less.cate[, 9]))
```

## IsOnlineSale
```{r bar10, echo=FALSE}
ggplotly(bar(less.cate[, 10]))
```

#Plots of Continuous Variables{.tabset .tabset-dropdown}

## VehOdo
```{r VehOdo, echo=FALSE}
ggplot(cars, aes(x=IsBadBuy, y=VehOdo, color =IsBadBuy, group=IsBadBuy))+geom_boxplot()+coord_cartesian(xlim = c(-1, 2))+coord_flip()
ggplot(cars, aes(x=cars$VehOdo, fill=as.character(((as.numeric(as.character(cars$IsBadBuy)))+1)*3)))+ geom_density(alpha=.3)+ scale_fill_discrete(name = "IsBadBuy", labels = c("Good", "Bad"))
```

## VehBCost
```{r VehBCost, echo=FALSE}
ggplot(cars, aes(x=IsBadBuy, y=VehBCost, color =IsBadBuy, group=IsBadBuy)) +geom_boxplot()+coord_cartesian(xlim = c(-1, 2))+coord_flip()
ggplot(cars, aes(x=cars$VehBCost, fill=as.character(((as.numeric(as.character(cars$IsBadBuy)))+1)*3)))+ geom_density(alpha=.3)+ scale_fill_discrete(name = "IsBadBuy", labels = c("Good", "Bad"))
```

## WarrantyCost
```{r WarrantyCost, echo=FALSE}
ggplot(cars, aes(x=IsBadBuy, y=WarrantyCost, color =IsBadBuy, group=IsBadBuy))+geom_boxplot()+coord_cartesian(xlim = c(-1, 2))+coord_flip()
ggplot(cars, aes(x=cars$WarrantyCost, fill=as.character(((as.numeric(as.character(cars$IsBadBuy)))+1)*3)))+ geom_density(alpha=.3)+ scale_fill_discrete(name = "IsBadBuy", labels = c("Good", "Bad"))
```

## MMRAcquisitionAuctionAveragePrice
```{r MMRAcquisitionAuctionAveragePrice, echo=FALSE}
mis <- which(MMRCurrentAuctionAveragePrice %in% NA)
pIsBadBuy <- IsBadBuy[-mis] 
pIsBadBuy <- as.factor(pIsBadBuy)
mMMRCurrentAuctionAveragePrice <- MMRCurrentAuctionAveragePrice[-mis]
data1 <- data.frame(c(1:length(mMMRCurrentAuctionAveragePrice)), ncol=2, nrow=length(mMMRCurrentAuctionAveragePrice))
data1[, 1] <- as.matrix(mMMRCurrentAuctionAveragePrice, ncol=1)
data1[, 2] <- as.matrix(pIsBadBuy, ncol=1)

ggplot(data1 , aes(x=pIsBadBuy,y=mMMRCurrentAuctionAveragePrice, color =pIsBadBuy, group=(as.factor(as.numeric(as.character(pIsBadBuy))))) )+scale_fill_discrete(labels = c("Good", "Bad"))+geom_boxplot() +coord_flip()

ggplot(data1, aes(x=mMMRCurrentAuctionAveragePrice, fill=as.character(((as.numeric(as.character(pIsBadBuy)))+1)*3)))+ geom_density(alpha=.3)+ scale_fill_discrete(name = "IsBadBuy", labels = c("Good", "Bad"))
```

## MMRAcquisitionAuctionCleanPrice
```{r MMRAcquisitionAuctionCleanPrice, echo=FALSE}
mis <- which(MMRAcquisitionAuctionCleanPrice %in% NA)

pIsBadBuy <- IsBadBuy[-mis] 
pIsBadBuy <- as.factor(pIsBadBuy)
mMMRAcquisitionAuctionCleanPrice <- MMRAcquisitionAuctionCleanPrice[-mis]
data1 <- data.frame(c(1:length(mMMRAcquisitionAuctionCleanPrice)), ncol=2, nrow=length(mMMRAcquisitionAuctionCleanPrice))
data1[, 1] <- as.matrix(mMMRAcquisitionAuctionCleanPrice, ncol=1)
data1[, 2] <- as.matrix(pIsBadBuy, ncol=1)

ggplot(data1 , aes(x=pIsBadBuy,y=mMMRAcquisitionAuctionCleanPrice, color =pIsBadBuy, group=pIsBadBuy ))+geom_boxplot()+coord_flip()
ggplot(data1, aes(x=mMMRAcquisitionAuctionCleanPrice, fill=as.character(((as.numeric(as.character(pIsBadBuy)))+1)*3)))+ geom_density(alpha=.3)+ scale_fill_discrete(name = "IsBadBuy", labels = c("Good", "Bad"))
```

## MMRAcquisitionRetailAveragePrice
```{r MMRAcquisitionRetailAveragePrice2, echo=FALSE}
mis <- which(MMRAcquisitionRetailAveragePrice %in% NA)

pIsBadBuy <- IsBadBuy[-mis] 
pIsBadBuy <- as.factor(pIsBadBuy)
mMMRAcquisitionRetailAveragePrice <- MMRAcquisitionRetailAveragePrice[-mis]
data1 <- data.frame(c(1:length(mMMRAcquisitionRetailAveragePrice)), ncol=2, nrow=length(mMMRAcquisitionRetailAveragePrice))
data1[, 1] <- as.matrix(mMMRAcquisitionRetailAveragePrice, ncol=1)
data1[, 2] <- as.matrix(pIsBadBuy, ncol=1)

ggplot(data1 , aes(x=pIsBadBuy,y=mMMRAcquisitionRetailAveragePrice, color =pIsBadBuy, group=pIsBadBuy ))+geom_boxplot()+coord_flip()
ggplot(data1, aes(x=mMMRAcquisitionRetailAveragePrice, fill=as.character(((as.numeric(as.character(pIsBadBuy)))+1)*3)))+ geom_density(alpha=.3)+ scale_fill_discrete(name = "IsBadBuy", labels = c("Good", "Bad"))
```

## MMRAcquisitionRetailCleanPrice
```{r MMRAcquisitionRetailCleanPrice, echo=FALSE}
mis <- which(MMRAcquisitionRetailCleanPrice %in% NA)

pIsBadBuy <- IsBadBuy[-mis] 
pIsBadBuy <- as.factor(pIsBadBuy)
mMMRAcquisitionRetailCleanPrice <- MMRAcquisitionRetailCleanPrice[-mis]
data1 <- data.frame(c(1:length(mMMRAcquisitionRetailCleanPrice)), ncol=2, nrow=length(mMMRAcquisitionRetailCleanPrice))
data1[, 1] <- as.matrix(mMMRAcquisitionRetailCleanPrice, ncol=1)
data1[, 2] <- as.matrix(pIsBadBuy, ncol=1)

ggplot(data1 , aes(x=pIsBadBuy,y=mMMRAcquisitionRetailCleanPrice, color =pIsBadBuy, group=pIsBadBuy ))+geom_boxplot()+coord_flip()
ggplot(data1, aes(x=mMMRAcquisitionRetailCleanPrice, fill=as.character(((as.numeric(as.character(pIsBadBuy)))+1)*3)))+ geom_density(alpha=.3)+ scale_fill_discrete(name = "IsBadBuy", labels = c("Good", "Bad"))
```

## MMRCurrentAuctionAveragePrice
```{r MMRCurrentAuctionAveragePrice, echo=FALSE}
mis <- which(MMRCurrentAuctionAveragePrice %in% NA)

pIsBadBuy <- IsBadBuy[-mis] 
pIsBadBuy <- as.factor(pIsBadBuy)
mMMRCurrentAuctionAveragePrice <- MMRCurrentAuctionAveragePrice[-mis]
data1 <- data.frame(c(1:length(mMMRCurrentAuctionAveragePrice)), ncol=2, nrow=length(mMMRCurrentAuctionAveragePrice))
data1[, 1] <- as.matrix(mMMRCurrentAuctionAveragePrice, ncol=1)
data1[, 2] <- as.matrix(pIsBadBuy, ncol=1)

ggplot(data1 , aes(x=pIsBadBuy,y=mMMRCurrentAuctionAveragePrice, color =pIsBadBuy, group=pIsBadBuy ))+geom_boxplot()+coord_flip()
ggplot(data1, aes(x=mMMRCurrentAuctionAveragePrice, fill=as.character(((as.numeric(as.character(pIsBadBuy)))+1)*3)))+ geom_density(alpha=.3)+ scale_fill_discrete(name = "IsBadBuy", labels = c("Good", "Bad"))
```

## MMRCurrentAuctionCleanPrice
```{r MMRCurrentAuctionCleanPrice, echo=FALSE}
mis <- which(MMRCurrentAuctionCleanPrice %in% NA)

pIsBadBuy <- IsBadBuy[-mis] 
pIsBadBuy <- as.factor(pIsBadBuy)
mMMRCurrentAuctionCleanPrice <- MMRCurrentAuctionCleanPrice[-mis]
data1 <- data.frame(c(1:length(mMMRCurrentAuctionCleanPrice)), ncol=2, nrow=length(mMMRCurrentAuctionCleanPrice))
data1[, 1] <- as.matrix(mMMRCurrentAuctionCleanPrice, ncol=1)
data1[, 2] <- as.matrix(pIsBadBuy, ncol=1)

ggplot(data1 , aes(x=pIsBadBuy,y=mMMRCurrentAuctionCleanPrice, color =pIsBadBuy, group=pIsBadBuy ))+geom_boxplot()+coord_flip()
ggplot(data1, aes(x=mMMRCurrentAuctionCleanPrice, fill=as.character(((as.numeric(as.character(pIsBadBuy)))+1)*3)))+ geom_density(alpha=.3)+ scale_fill_discrete(name = "IsBadBuy", labels = c("Good", "Bad"))

```

## MMRCurrentRetailAveragePrice
```{r MMRCurrentRetailAveragePrice, echo=FALSE}
mis <- which(MMRCurrentRetailAveragePrice %in% NA)

pIsBadBuy <- IsBadBuy[-mis] 
pIsBadBuy <- as.factor(pIsBadBuy)
mMMRCurrentRetailAveragePrice <- MMRCurrentRetailAveragePrice[-mis]
data1 <- data.frame(c(1:length(mMMRCurrentRetailAveragePrice)), ncol=2, nrow=length(mMMRCurrentRetailAveragePrice))
data1[, 1] <- as.matrix(mMMRCurrentRetailAveragePrice, ncol=1)
data1[, 2] <- as.matrix(pIsBadBuy, ncol=1)

ggplot(data1 , aes(x=pIsBadBuy,y=mMMRCurrentRetailAveragePrice, color =pIsBadBuy, group=pIsBadBuy ))+geom_boxplot()+coord_flip()
ggplot(data1, aes(x=mMMRCurrentRetailAveragePrice, fill=as.character(((as.numeric(as.character(pIsBadBuy)))+1)*3)))+ geom_density(alpha=.3)+ scale_fill_discrete(name = "IsBadBuy", labels = c("Good", "Bad"))
```

## MMRCurrentRetailCleanPrice
```{r MMRCurrentRetailCleanPrice, echo=F}
mis <- which(MMRCurrentRetailCleanPrice %in% NA)

pIsBadBuy <- IsBadBuy[-mis] 
pIsBadBuy <- as.factor(pIsBadBuy)
mMMRCurrentRetailCleanPrice <- MMRCurrentRetailCleanPrice[-mis]
data1 <- data.frame(c(1:length(mMMRCurrentRetailCleanPrice)), ncol=2, nrow=length(mMMRCurrentRetailCleanPrice))
data1[, 1] <- as.matrix(mMMRCurrentRetailCleanPrice, ncol=1)
data1[, 2] <- as.matrix(pIsBadBuy, ncol=1)

ggplot(data1 , aes(x=pIsBadBuy,y=mMMRCurrentRetailCleanPrice, color =pIsBadBuy, group=pIsBadBuy ))+geom_boxplot()+coord_flip()
ggplot(data1, aes(x=mMMRCurrentRetailCleanPrice, fill=as.character(((as.numeric(as.character(pIsBadBuy)))+1)*3)))+ geom_density(alpha=.3)+ scale_fill_discrete(name = "IsBadBuy", labels = c("Good", "Bad"))
```